ML parameters

### 2022-09-19 workflow/notebooks/ml-params.Rmd
TODO: compare OTU vs genus level

- `trainfrac`: training set size as a fraction(`0.65`, `0.8`)
- `dataset`: all samples for all outcomes (`full`) vs intersection of outcomes not missing (`int`) 
- `method`: random forest (`rf`) vs L2 logistic regression (`glmnet`)
- `metric`: optimize model for `AUROC` vs `F1`

>>>>

- `trainfrac`: training set size as a fraction(`0.65`, `0.8`)
- `dataset`: all samples for all outcomes (`full`) vs intersection of outcomes not missing (`int`) 
- `method`: random forest (`rf`) vs L2 logistic regression (`glmnet`)
- `metric`: optimize model for `AUROC` vs `F1`
- taxonomic level: OTU vs genus. TODO: train models on genus level features
